Insights Into Computational Reproducibility in Plant Pathology and a Way Forward

### 2020-12-07 analysis/paper/paper.Rmd
Add description of data availability results and corresponding table

@@

>>>>

Likewise, data availability was mostly not available with 243 or 81.5% scoring "0" where the data was not available or mentioned in the article.
However, more articles, 29 or 9.7%, scored "3" than "1" or "2" combined, with two articles not producing shareable data (Table \@ref(tab:da)).

@@

```{r data_available, tab.id="da", tab.cap="Article ratings for data availability where '0', not specified or mentioned in publication to '3', Freely available online to anonymous users for foreseeable future (_e.g._ archived using Zenodo, dataverse or university library or some other proper archiving system).", echo=FALSE, message=FALSE, warning=FALSE}
import_notes() %>%
  tabyl(data_avail) %>%
  adorn_pct_formatting() %>% 
  select(-percent) %>% 
  rename(`data availability` = data_avail,
         percent = valid_percent) %>% 
  flextable() %>%
  autofit()
```
